Inspect Different Length Sample Size impact on ISS 2.2

### 2024-09-24 Rmd/Inspect_Outputs/change_sample_size_2.2.Rmd
inspect N=20. results as expected.

---
title: "Inspect Different Length Sample Size impact on ISS 2.1"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

# speed: this took ~1000 seconds
out.10 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_10_ISS_100iters_output_2024-09-23.RDS")

# speed: this took ~1000 seconds
out.N = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_.N_ISS_100iters_output_2024-09-23.RDS")

# speed: this took ~1000 seconds
out.30 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_30_ISS_100iters_output_2024-09-23.RDS")

@@

# Introduction
Plot the ISS resulting from three levels of haul-level sample size:
1. 10
2. length(flex.vec)
3. 30

@@

@@

# Conclusion
similar to last run.

>>>>

---
title: "Inspect Different Length Sample Size impact on ISS 2.2"
author: "Brett Stacy"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

out.10 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_10_ISS_100iters_output_2024-09-23.RDS")

out.N = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_.N_ISS_100iters_output_2024-09-23.RDS")

out.20 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.5_N_samples_20_ISS_100iters_output_2024-09-24.RDS")

out.30 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/haul_sample_size_change_V2.4_N_samples_30_ISS_100iters_output_2024-09-23.RDS")

@@

# Introduction
Plot the ISS resulting from three levels of haul-level sample size:
1. 10
2. 20
3. 30

@@

# 30
(out.20$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% 
  plot(type = "l")
(out.20$length$iss$iss/out.N$length$iss$iss) %>% round(digits = 2) %>% mean

@@

# Conclusion
looks reasonable.
